### 2020-04-03 writeup/setup.tex
sec 3 wip
sec 3.1 wip

First, we provide a complete and precise picture for when there is positive vs negative transfer in the setting of learning two tasks.
\begin{enumerate}
	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.
	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
	\item {\bf Negative transfer from model shift:} we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks.
\end{enumerate}

@@

\paragraph{The case of two tasks.}
From \cite{WZR20}, we know that either we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
Following \cite{WZR20}, for the rest of the paper, we shall consider the case when $r=1$ since there are only two tasks.
Here, equation \eqref{eq_mtl} simplifies to the following
\[ f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2, \]
where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
To solve the above, suppose that $w_1, w_2$ are fixed, by local optimality, we solve $B$ as
\begin{align*}
	\hat{B}(w) &= (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2),
\end{align*}
where we denote $w = w_1 / w_2$.
As a remark, when $w = 1$, we recover the linear regression estimator.
The test error of using $w_2 \hat{B}(w)$ for the target task is
\begin{align}
	\te(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
			&~ + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl}
\end{align}
In the above, the first is a bias term introduced by the model shift between the source and target tasks.
The second is a variance term, which decreases monotonically as we add more and more source task data.
Let $\hat{w}$ denote the minimizer of $te(w_2 \hat{B})$ over $w\in\real$.
Note that we can obtain the value of $\te(w_1\hat{B})$ through a validation set.
We will denote $\hat{\beta}_t^{\MTL} = w_2 \hat{B}(\hat{w})$.

@@

>>>>

First, we provide a complete and precise picture for when there is positive vs negative transfer in the setting of learning two tasks.
\begin{enumerate}
	\item {\bf De-noising effect of MTL:} we show that multi-task learning has a de-noising effect of reducing the variance of the estimator.
	When this variance reduction effect is bigger than the bias caused by model shift, we get positive transfer.

	{\bf Negative transfer from model shift:} To complement the above result, we establish a fundamental limit of multi-task learning compared to single-task learning in the presence of model shift.
	The phenomenon of negative transfer persists despite changing the model capacity or reweighting the tasks.
	\item {\bf Covariate shift affects the rate of transfer:} we further show that covariate shift can control the rate in which transfer occurs.
\end{enumerate}

@@

\paragraph{The case of two tasks.}
From \cite{WZR20}, we know that either we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
Following \cite{WZR20}, for the rest of the paper, we shall consider the case when $r=1$ since there are only two tasks.
Here, equation \eqref{eq_mtl} simplifies to the following
\[ f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2, \]
where $B\in\real^p$ and $w_1, w_2$ are both real numbers.
To solve the above, suppose that $w_1, w_2$ are fixed, by local optimality, we solve $B$ as
\begin{align*}
	\hat{B}(w) &= (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \\
	&= \frac{1}{w_2} (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} (w X_1^{\top}Y_1 + X_2^{\top}Y_2) \\
	&= \frac{1}{w_2}\bigbrace{\beta_t + (w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\bigbrace{X_1^{\top}X_1(w\beta_s - w^2\beta_t) + (w X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2)}},
\end{align*}
where we denote $w = w_1 / w_2$.
As a remark, when $w = 1$, we recover the linear regression estimator.
The test error of using $w_2 \hat{B}(w)$ for the target task is
\begin{align}
	\te(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
			&~ + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl}
\end{align}
In the above, the first is a bias term introduced by the model shift between the source and target tasks.
The second is a variance term, which decreases monotonically as we add more and more source task data.
Let $\hat{w}$ denote the minimizer of $te(w_2 \hat{B})$ over $w\in\real$.
Note that we can obtain the value of $\te(w_1\hat{B})$ through a validation set.
We will denote $\hat{\beta}_t^{\MTL} = w_2 \hat{B}(\hat{w})$.

@@

\begin{lemma}\label{lem_minv}
	In the setting when $n_2 = c_2 p$ we have that as $p$ goes to infinity,
	\[ \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{n_2 - p}\bigtr{\Sigma_2^{-1}}. \]
\end{lemma}
